Combined annotation exploration for SCPCP000006

### 2024-11-06 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
re-render the 07 notebook with updated results

- the predicted CNV calculated using intra-sample endothelial and immune cells (`--reference both`) as normal reference

@@

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)

# Create a data frames of all annotations
cell_type_df <- unique(metadata$scpca_sample_id) |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # This sample was run with "none" for reference
      if (sample_id == "SCPCS000190") {
        reference <- "none"
      } else {
        reference <- "both"
      }
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("06_infercnv_HMM-i3_{sample_id}_reference-{reference}.rds")
      )

>>>>

- the predicted CNV calculated using intra-sample endothelial and immune cells (`--reference both`) as normal reference; no reference was used for samples with fewer than 3 predicted normal cells.

@@

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE)
sample_ids <- metadata |>
  dplyr::filter(seq_unit != "spot") |>
  dplyr::pull(scpca_sample_id) |>
  unique()

# Create a data frames of all annotations
cell_type_df <- sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # These samples were run with "none" as the reference
      none_reference_samples <- c("SCPCS000177", "SCPCS000180", "SCPCS000181", "SCPCS000190", "SCPCS000197")
      if (sample_id %in% none_reference_samples) {
        reference <- "none"
      } else {
        reference <- "both"
      }
      input_file <- file.path(
        result_dir,
        sample_id,
        glue::glue("06_infercnv_HMM-i3_{sample_id}_reference-{reference}.rds")
      )
